---
title: "Health Facility Survey 2021: The MalCon Monitoring Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
source("scripts/dash_setup.R")
library(flexdashboard)
```

Summary
=======================================================================

Column { data-width=150 }
-----------------------------------------------------------------------

### Survey Progress - `r province_complete` / 22 provinces completed {.gauge}

```{r}
### Success Rate
gauge(
    province_complete_pct, min = 0, max = 100, symbol = '%', 
    sectors = gaugeSectors(
      danger = c(0, 20),
      warning = c(20, 80),
      success = c(80, 100)
    )
  )  
```

### Last Submission Date {.value-box}
```{r}
valueBox(value = last_submission$hfs_00X[1], 
         caption = "Date of last submission", 
         icon = "fas fa-calendar", 
         color = tested_color)
```

### Team that made last submission

```{r}
last_submission <- last_submission %>% 
    dplyr::mutate(
        team = NA,
        team = ifelse(hfs_007 %in% c("Clara_Are", "Wilbert_Neiembe", 
                                     "Florence_Lawrence"), 1, team),
        team = ifelse(hfs_007 %in% c("Jacob_Girupano", "Melvin_Kualawi"), 2, team),
        team = ifelse(hfs_007 %in% c("Micah_Muri", "Ismart_Martin"), 3, team)
    )  
valueBox(value = paste0("Team ", last_submission$team[1]), 
         caption = "made last submission", 
         icon = "fas fa-upload", 
         color = positive_color)
```

### Total health facility completed {.value-box}

```{r}
valueBox(value = sum(hf_num$n), 
         caption = "Total HF completed", 
         icon = "fas fa-hospital", 
         color = recovered_color)
```

### Total health center completed {.value-box}

```{r}
valueBox(value = hf_num$n[2], 
         caption = "Total HC completed", 
         icon = "fas fa-procedures", 
         color = death_color)
```


### Total aid post completed {.value-box}

```{r}
valueBox(value = hf_num$n[1], 
         caption = "Total AP completed", 
         icon = "fas fa-heartbeat", 
         color = h_symptoms_color)
```



Column {data-width=625}
-----------------------------------------------------------------------

### Survey Progress by Province (as of `r last_submission$hfs_00X[1]`)

```{r}
# png_map %>% 
#     dplyr::mutate(province = toupper(province), 
#                   n = ifelse(is.na(n), 0, n)) %>%
#     dplyr::rename(`No. HF completed` = n) %>% 
#     mapview::mapview(zcol = "No. HF completed")
```


Column {data-width=500}
-----------------------------------------------------------------------

### Total no. of forms submitted

```{r}
library(ggplot2)
form_submit %>% 
    ggplot(aes(fid, num, fill = fid)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label=num), position=position_dodge(width=0.9), vjust=-0.25) + 
    labs(title = "", x = "Form id", y = "Number submitted") +
    theme(legend.position="none")
```   

### Total no. of forms submitted by survey teams 

```{r}
dplyr::bind_rows(
    hfc_v3 %>% 
        dplyr::select(hfs_007, hfs_001A) %>% 
        dplyr::mutate(form = 1), 
    pi_v3 %>% 
        dplyr::select(hfs_007, hfs_001A) %>% 
        dplyr::mutate(form = 2), 
    ppa_v3 %>% 
        dplyr::select(hfs_007, hfs_001A) %>% 
        dplyr::mutate(form = 3), 
    ei_v3 %>% 
        dplyr::select(hfs_007, hfs_001A) %>% 
        dplyr::mutate(form = 4)
) %>% 
    dplyr::mutate(
        team = NA,
        team = ifelse(hfs_007 %in% c("Clara_Are", "Wilbert_Neiembe", 
                                     "Florence_Lawrence"), 1, team),
        team = ifelse(hfs_007 %in% c("Jacob_Girupano", "Melvin_Kualawi"), 2, team),
        team = ifelse(hfs_007 %in% c("Micah_Muri", "Ismart_Martin"), 3, team)
    ) %>% 
    dplyr::group_by(team, form) %>%
    dplyr::summarise(n = dplyr::n()) %>% 
    dplyr::ungroup() %>%
    dplyr::mutate(team = factor(team), 
                  form = paste0("form_", form)) %>%
    tidyr::spread(form, n) %>% 
    
    plotly::plot_ly(y = ~ team, 
          x = ~ form_1, 
          orientation = 'h',
          text =  ~ form_1,
          textposition = 'auto',
          type = "bar", 
          name = "Form 1",
          marker = list(color = "#1f77b4")) %>% 
    plotly::add_trace(x = ~ form_2,
            text =  ~ form_2,
            textposition = 'auto',
            name = "Form 2",
            marker = list(color = "forestgreen")) %>%
    plotly::add_trace(x = ~ form_2, 
            text =  ~ form_2,
            textposition = 'auto',
            name = "Form 3",
            marker = list(color = "red")) %>%
    plotly::layout(title = "",
            barmode = 'stack',
            yaxis = list(title = "Teams"),
            xaxis = list(title = "Number of forms submitted by type"),
            hovermode = "compare",
            legend = list(x = 0.7, y = 0.5),
            margin =  list(
               l = 20,
               r = 10,
               b = 10,
               t = 30,
               pad = 2
             )
        )

 # %>%
 #  layout( xaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)),
 #          yaxis = list(titlefont = list(size = 22), tickfont = list(size = 22)) )
```   


Field Visit Summary
=======================================================================

Column {.tabset .tabset-fade}
-------------------------------------
   
### Overall issues

```{r}
fvs_v1 <- fvs_v1 %>% 
    dplyr::mutate(hfs_00XA = paste("Team ", hfs_00XA), 
                  hfs_00X = as.Date(sub("T.*", "", hfs_00X), format = "%Y-%m-%d"))
fvs_v1 %>% 
    dplyr::select(hfs_00X, hfs_00XA, hfs_001A, hfs_46) %>%  
    dplyr::filter(!grepl("nil|none|success", 
                         tolower(hfs_46))) %>% 
    dplyr::arrange(dplyr::desc(hfs_00X)) %>% 
    dplyr::rename(`submission date` = hfs_00X, 
                  team = hfs_00XA, 
                  province = hfs_001A,
                  issue = hfs_46) %>% 
    DT::datatable(rownames = FALSE, 
                options = list(searchHighlight = TRUE, scrollY = '600px'), 
                filter = 'top',)
```

### Issue with field budgets

```{r}
fvs_v1 %>% 
    dplyr::select(hfs_00X, hfs_00XA, hfs_001A, hfs_43) %>% 
    dplyr::filter(!grepl("nil|none|no issue|did not encounter|wasn't any|wasnt", 
                         tolower(hfs_43))) %>% 
    dplyr::arrange(dplyr::desc(hfs_00X)) %>% 
    dplyr::rename(`submission date` = hfs_00X, 
                  team = hfs_00XA, 
                  province = hfs_001A, 
                  issue = hfs_43) %>% 
    DT::datatable(rownames = FALSE, 
                options = list(searchHighlight = TRUE, scrollY = '600px'), 
                filter = 'top',)
```   
 
### Stock-out of field supplies
    
```{r}
fvs_v1 %>% 
    dplyr::select(hfs_00X, hfs_00XA, hfs_001A, hfs_44) %>%
    dplyr::filter(!grepl("nil|none|no stock-out|not stock-out|did not have|no stockout|was not|did not|were not|no stock|wasn't|wasnt", 
                         tolower(hfs_44))) %>% 
    dplyr::arrange(dplyr::desc(hfs_00X)) %>% 
    dplyr::rename(`submission date` = hfs_00X, 
                  team = hfs_00XA, 
                  province = hfs_001A, 
                  issue = hfs_44) %>% 
    DT::datatable(rownames = FALSE, 
                options = list(searchHighlight = TRUE, scrollY = '600px'), 
                filter = 'top',)
```

### Incident of transportation

```{r}
fvs_v1 %>% 
    dplyr::select(hfs_00X, hfs_00XA, hfs_001A, hfs_45) %>%  
    dplyr::filter(!grepl("nil|none|did not have|was not|did not|were not|no|wasn't|wasnt", 
                         tolower(hfs_45))) %>% 
    dplyr::arrange(dplyr::desc(hfs_00X)) %>% 
    dplyr::rename(`submission date` = hfs_00X, 
                  team = hfs_00XA, 
                  province = hfs_001A,
                  issue = hfs_45) %>% 
    DT::datatable(rownames = FALSE, 
                options = list(searchHighlight = TRUE, scrollY = '600px'), 
                filter = 'top',)
```


About
=======================================================================
**The MalCon Monitoring Dashboard**

This [MalCon Monitoring Dashboard](https://myominnoo.github.io/malcon-dash/) provides an overview of the progress of the health facility survey 2021 conducted by the Malaria Control Section (MalCon) at the Papua New Guinea Institute of Medical Research (PNGMIR). This dashboard is built in the framework of reproducibile research using Rmarkdown and GitHub action workflows.

**Data**

The input data for this dashboard are from the ODK Central platform that is hosted by Swiss Tropical and Public Health Institute. The data and dashboard are refreshed on a daily basis.

**Packages**

- Dashboard interface - the `flexdashboard` package.
- Visualization - the `plotly` package for the plots and mapview package for the map
- Data manipulation - `dplyr`, and `tidyr`
- Tables - the `DT` package

**Credits**
The projects by [Rami Krispin](https://github.com/RamiKrispin/) inspires this dashboard. 
