---
title: "The MalCon Monitoring Dashboard: Health Facility Survey `2021`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
source("scripts/data_refresh.R")
library(flexdashboard)
```

Summary
=======================================================================

Column { data-width=150 }
-----------------------------------------------------------------------

### Survey Progress in `r province_complete` / 22 provinces {.gauge}

```{r}
### Success Rate
gauge(
    province_complete_pct, min = 0, max = 100, symbol = '%', 
    sectors = gaugeSectors(
      danger = c(0, 20),
      warning = c(20, 80),
      success = c(80, 100)
    )
  )  
```

### Last Submission Date {.value-box}
```{r}
last_submit_date <- last_submission$hfs_000X[1]
valueBox(value = last_submit_date, 
         caption = "Date of last submission", 
         icon = "fas fa-calendar", 
         color = tested_color)
```

### Team that made last submission

```{r}
valueBox(value = paste0("Team ", last_submission$team[1]), 
         caption = "made last submission", 
         icon = "fas fa-upload", 
         color = positive_color)
```

### Total health facility completed {.value-box}

```{r}
hf_total <- sum(hf_type$n)
valueBox(value = hf_total, 
         caption = "Total Health Facilities (HF) surveyed", 
         icon = "fas fa-hospital", 
         color = recovered_color)
```

### Total health center completed {.value-box}

```{r}
hf_hc <- paste0(hf_type$n[2], " (", round(hf_type$n[2]/hf_total*100, 0), "%)")
valueBox(value = hf_hc,
         caption = paste0("Health centers out of ", hf_total, " HF"), 
         icon = "fas fa-procedures", 
         color = death_color)
```


### Total aid post completed {.value-box}

```{r}
hf_ap <- paste0(hf_type$n[1], " (", round(hf_type$n[1]/hf_total*100, 0), "%)")
valueBox(value = hf_ap, 
         caption = paste0("Aid posts out of ", hf_total, " HF"),
         icon = "fas fa-heartbeat", 
         color = h_symptoms_color)
```


### Total hospital completed {.value-box}

```{r}
hf_hosp <- paste0(hf_type$n[3], " (", round(hf_type$n[3]/hf_total*100, 0), "%)")
valueBox(value = hf_hosp, 
         caption = paste0("Hospitals out of ", hf_total, " HF"),
         icon = "fas fa-heartbeat", 
         color = "blue")
```


Column {data-width=625}
-----------------------------------------------------------------------
    
### Survey Progress by Province (as of `r last_submit_date`)

Note that the figures for **Hela** and **Jiwaka** are combined with those of **Southern Highlands** and **Chimbu** because the `rnaturalearth` package only allows `20` provinces instead of `22`. 

```{r}
clrs <- c("ffffff", "ffbe0b",
          "8338ec", "8338ec", "3a86ff", "38b000")
png_map %>%
    dplyr::rename(`No. HF completed` = n) %>%
    mapview::mapview(zcol = "No. HF completed", 
                     col.regions = paste("#", clrs, sep = ""))
```


Column {data-width=500}
-----------------------------------------------------------------------
    
### Total no. of forms submitted

```{r}
library(ggplot2)
form_submit %>% 
    ggplot(aes(fid, num, fill = fid)) +
    geom_bar(stat = "identity") +
    geom_text(aes(label=num), position=position_dodge(width=0.9), vjust=-0.25) + 
    scale_fill_manual(
        "legend", 
        values = c("form1" = "#f94144", "form2" = "#f3722c", 
                   "form3" = "#90be6d", "form4" = "#277da1")
    ) + 
    labs(title = "", x = "Form ID", y = "No. of forms submitted") +
    theme(legend.position="none")
```   

### Total no. of forms submitted by survey teams 

```{r}
dplyr::bind_rows(
    hfc %>% 
        dplyr::select(hfs_010, hfs_001A) %>% 
        dplyr::mutate(form = 1), 
    pi %>% 
        dplyr::select(hfs_010, hfs_001A) %>% 
        dplyr::mutate(form = 2), 
    ppa %>% 
        dplyr::select(hfs_010, hfs_001A) %>% 
        dplyr::mutate(form = 3), 
    ei %>% 
        dplyr::select(hfs_010, hfs_001A) %>% 
        dplyr::mutate(form = 4)
) %>% 
    dplyr::mutate(
        team = NA,
        team = ifelse(hfs_010 %in% team1, 1, team),
        team = ifelse(hfs_010 %in% team2, 2, team),
        team = ifelse(hfs_010 %in% team3, 3, team),
        team = ifelse(hfs_010 %in% team4, 4, team)
    ) %>% 
    dplyr::group_by(team, form) %>%
    dplyr::summarise(n = dplyr::n()) %>% 
    dplyr::ungroup() %>%
    dplyr::mutate(team = factor(team), 
                  form = paste0("form_", form)) %>%
    tidyr::spread(form, n) %>% 
    
    plotly::plot_ly(y = ~ team, 
                    x = ~ form_1, 
                    orientation = 'h',
                    text =  ~ form_1,
                    textposition = 'auto',
                    type = "bar", 
                    name = "Form 1: Health Facility Checklist",
                    marker = list(color = "#f94144")) %>% 
    plotly::add_trace(x = ~ form_2,
                      text =  ~ form_2,
                      textposition = 'auto',
                      name = "Form 2: Provider Interview",
                      marker = list(color = "#f3722c")) %>%
    plotly::add_trace(x = ~ form_3, 
                      text =  ~ form_3,
                      textposition = 'auto',
                      name = "Form 3: Patient Provider Assessment",
                      marker = list(color = "#90be6d")) %>%
    plotly::add_trace(x = ~ form_4, 
                      text =  ~ form_4,
                      textposition = 'auto',
                      name = "Form 4: Exit Interview",
                      marker = list(color = "#277da1")) %>%
    plotly::layout(title = "",
                   barmode = 'stack',
                   yaxis = list(title = "Teams"),
                   xaxis = list(title = "Number of forms submitted by type"),
                   hovermode = "compare",
                   legend = list(x = 0.4, y = 0.5),
                   margin =  list(
                       l = 20,
                       r = 10,
                       b = 10,
                       t = 30,
                       pad = 2
                   )
    ) 
```   


Field Visit Summary
=======================================================================
    
    Column {.tabset .tabset-fade}
-------------------------------------
    
### Overall issues
    
```{r}
overall %>% 
    DT::datatable(rownames = FALSE, 
                  options = list(searchHighlight = TRUE, scrollY = '600px'), 
                  filter = 'top',)
```

### Issue with field budgets

```{r}
budgets %>% 
    DT::datatable(rownames = FALSE, 
                  options = list(searchHighlight = TRUE, scrollY = '600px'), 
                  filter = 'top',)
```   

### Stock-out of field supplies

```{r}
supplies %>% 
    DT::datatable(rownames = FALSE, 
                  options = list(searchHighlight = TRUE, scrollY = '600px'), 
                  filter = 'top',)
```

### Incident of transportation

```{r}
transport %>% 
    DT::datatable(rownames = FALSE, 
                  options = list(searchHighlight = TRUE, scrollY = '600px'), 
                  filter = 'top',)
```




About
=======================================================================
**The MalCon Monitoring Dashboard**
    
This [MalCon Monitoring Dashboard](https://myominnoo.github.io/malcon-dash/) provides an overview of the progress of the `health facility survey 2021` that is being conducted by the Malaria Control Section (`MalCon`) at the `Papua New Guinea Institute of Medical Research` (`PNGMIR`). 

This dashboard is built in the framework of reproducibile research using `Rmarkdown` and `GitHub action workflow`.

**Data**
    
The input data for this dashboard is the [Data Automation site](https://github.com/myominnoo/malcon) which is a private repository on `GitHub` that is only accessible by the `MalCon` team. This repository retrieves daily data updates from the `ODK Central` platform hosted by the `Swiss TPH`. 

The updated data are then being passed through a series of data processing procedures in `R` and the final data are displayed as numbers and figures on the dashboard. 


**Technical Notes**

This dashboard is built with R using [Rmakrdown](https://rmarkdown.rstudio.com/) and [flexdashboard](https://rmarkdown.rstudio.com/flexdashboard/) framework, and can easily reproduce by others. The code behind the dashboard available [here](https://github.com/myominnoo/malcon-dash)

- `GitHub Action Workflow` for automated tasks
- `docker` for reproducible environments
- `rmarkdown` for rendering the dashboard webpage
- `shell` scripting to bridge `GitHub Action Workflow`, `docker`, and `R`
- `git` for version control system 

**R Packages**

- `dplyr`, and `tidyr` for data wrangling
- `flexdashboard` for the dashboard interface
- `plotly` and `ggplot2` for the plots 
- `rnaturalearth`` and `mapview` for the PNG map
- `DT` for diplaying tabular data 

**Acknowledgement**

The projects by [Rami Krispin](https://github.com/RamiKrispin/) inspires this dashboard. 
