---
title: "HFS 2021 - MalCon"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, echo=TRUE}
#------------------ Packages ------------------

# install required packages
install.packages("flexdashboard", dependencies = TRUE)

# load required packages
library(flexdashboard)

`%>%` <- magrittr::`%>%`

# set global variables
hfc_v3 <- NULL
pi_v3 <- NULL
ppa_v3 <- NULL
ei_v3 <- NULL
fvs_v1 <- NULL


for (x in 1:length(fid)) {
    temp_file <- tempdir()
    
    temp_file <- paste(temp_file, "/", fid[x], ".csv", sep = "")
    download.file(paste("https://", pat_key, "@", raw_url, fid[x], ".csv", sep = ""), 
                  temp_file)
    
    assign(fid[x], read.csv(temp_file, stringsAsFactors = FALSE))
}
print(search())
print(installed.packages())
```


Summary
=======================================================================

Column { data-width=500 }
-----------------------------------------------------------------------

### Total Number of Cases by Region (as of `r Sys.Date()`)



Column { data-width=500 }
-----------------------------------------------------------------------

### Cases Distribution by Region


Data
=======================================================================

```{r}
hfc_v3 %>% 
  DT::datatable(rownames = FALSE,
            options = list(searchHighlight = TRUE, 
                           pageLength = nrow(hfc_v3)), filter = 'top')
```


About
=======================================================================
**The MalCon PNGIMR Dashboard**

This [MalCon PNGIMR Dashboard](https://myominnoo.github.io/malcon-dash/) provides an overview of the progress of the health facility survey 2021 conducted by the Malaria Control Section (MalCon) at the Papua New Guinea Institute of Medical Research (PNGMIR). This dashboard is built in the framework of reproducibile research using Rmarkdown and GitHub action workflows.

**Data**

The input data for this dashboard are from the ODK Central platform that is hosted by Swiss Tropical and Public Health Institute. The data and dashboard are refreshed on a daily basis.

**Packages**

- Dashboard interface - the flexdashboard package.
- Visualization - the plotly package for the plots and mapview package for the map
- Data manipulation - dplyr, and tidyr
- Tables - the DT package
